%-------------------------
% Resume in Latex
% Author : Laasya Aki
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingOneLine}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Laasya Aki}
 
\end{center}

\begin{center}
\href{mailto:laki@andrew.cmu.edu}{laki@andrew.cmu.edu} $|$
\small 612-417-5749 $|$
\href{https://www.linkedin.com/in/laasyaaki}{https://www.linkedin.com/in/laasyaaki} $|$
\href{http://laasyaaki.github.io}{http://laasyaaki.github.io}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Carnegie Mellon University}{May 2028}
        {Bachelor of Science in Computer Science, Concentration in Machine Learning}{GPA: 3.3}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Data Structures and Algorithms, Computer Systems, Functional Programming, Human-Computer Interaction, Intro to Robotics, Discrete Math, AI/Cybersecurity Independent Study}
     \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------Extracurriculars-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Dispatch}{May 2025 - Aug. 2025}
      {QA Automation Engineering Intern}{}
      \resumeItemListStart
        \resumeItem{Migrated mobile test suite from \textbf{Appium} to \textbf{Maestro Cloud} (\textbf{YAML}, \textbf{Ruby}, \textbf{JavaScript}, \textbf{AWS}), improving test reliability and reducing regression testing time by \textbf{40 hours} per 3-week sprint.}
        \resumeItem{Developed scalable, automated web test suites (\textbf{Playwright}, \textbf{Pytest}, \textbf{Python}), increasing coverage by \textbf{25\%}.}
        \resumeItem{Trained and deployed an \textbf{AI Agent} to convert legacy automation suites from \textbf{Selenium} to \textbf{Playwright}, automating the migration of \textbf{200+} test cases.}
      \resumeItemListEnd

    \resumeSubheading
      {Carnegie Mellon University}{Sept. 2024 - present}
      {AI and Cybersecurity Research Assistant, Software and Societal Systems Department}{}
      \resumeItemListStart
        \resumeItem{Constructing a \textbf{knowledge graph} of cyber defense playbooks (\textbf{Python}, \textbf{LLMs}, \textbf{RAG}, \textbf{MITRE D3FEND}) to map cyber defense techniques, enhancing automated threat response capabilities for an \textbf{NSA-funded project}.}
        \resumeItem{Designing a \textbf{dual-agent AI system} to autonomously test and validate the effectiveness of LLM-generated defense playbooks against simulated cyberattacks.}
        \resumeItem{Implementing a \textbf{rank-ordering algorithm} to evaluate defense playbook effectiveness in real-time, enabling adaptive response strategies based on situational threat analysis.}
      \resumeItemListEnd
      
    \resumeSubheading
      {General Mills}{June 2024 - Aug. 2024}
      {Digital \& Industrial Innovation IoT Intern}{}
      \resumeItemListStart
        \resumeItem{Prototyped \textbf{Industrial IoT (IIoT)} devices and platforms to create a scalable blueprint for integration into General Mills' future smart factory initiatives. }
        \resumeItem{Deployed and containerized applications with \textbf{Docker} to manage IIoT hardware.}
        \resumeItem{Designed interactive \textbf{Grafana dashboards} to interpret sensor data, providing key data-driven insights.}
      \resumeItemListEnd

    \resumeSubheading
      {Minnesota Twins}{May 2023 - Aug. 2023}
      {App Development Intern}{}
      \resumeItemListStart
        \resumeItem{Developed a full-stack web app (\textbf{React}, \textbf{TypeScript}, \textbf{Prisma}, \textbf{GCP}, \textbf{Tailwind CSS}) with \textbf{CRUD} functionality, saving sales executives \textbf{3 hours per week} by automating ticket assignments.}
        \resumeItem{Engineered \textbf{GraphQL endpoints} for employee and ticket data \textbf{APIs}, improving response times for over \textbf{10} apps.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS & LEADERSHIP-----------
\section{Projects and Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://cmueats.com}{CMUEats.com}}{May 2025 - present}
      {Tech Lead, CMU ScottyLabs}{}
      \resumeItemListStart
        \resumeItem{Leading 5-person development team for CMUEats.com (\textbf{React}, \textbf{Typescript}, \textbf{Vite}, \textbf{Elysia}), a web platform serving over \textbf{5,000 weekly users} at Carnegie Mellon.}
        \resumeItem{Collaborating with CMU Dining Services to ideate and develop new features, such as pinned locations and a sponsor carousel, to directly enhance user engagement.}
      \resumeItemListEnd

    \resumeSubheading
      {AgrID}{Jan 2023 - April 2023}
      {TechnovationMN Winner}{}
      \resumeItemListStart
        \resumeItem{Led 3-person team to develop a mobile app (\textbf{React Native}, \textbf{Firebase}, \textbf{Teachable Machine}) that identifies diseased crops using an \textbf{image classification ML model}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: Python, TypeScript/JavaScript, Java, C, Ruby, SQL, HTML/CSS, SML, x86-64 Assembly} \\
      \vspace{1mm}
      \textbf{Frameworks \& Libraries}{: React/React Native, Playwright, NodeJS, Pytest, Prisma, Tailwind CSS, Appium, Selenium} \\
      \vspace{1mm}
      \textbf{Tools \& Technologies}{: Git, Docker, AWS, GCP, PostgreSQL, GraphQL, REST APIs, CI/CD, Maestro Cloud, Jira, Figma, LLMs, RAG, Prompt Engineering, Firebase}
    }}
 \end{itemize}


\end{document}